Mass and occupation fraction of dark matter halos hosting Lyman-$\alpha$ emitters at $z\sim 3$

### 2013-11-20 paper/ms.tex
new figures in the paper

Figure \ref{fig:correlation_parameters} shows the main results for the
best estimates of $\theta_{0}-\beta$ in the parameterization of the
ACF. Blue circles represent the results from the mocks and the crosses
from observations. In the left panel Figure \ref{fig:correlation_parameters} we see
how the observational ACF measured by \cite{Hayashino2004} 
can be successful in reducing the total number of possible models. The
right panel shows the results for fields in the mock catalog with an
average number density compared against the fit of the data
reported by \cite{Ouchi2010}. In this case we find that there are
large uncertainties coming from the observational data, and only a reduced
fraction of the models can be discarded.

In Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
both for the comparisons against \cite{Hayashino2004} and
\cite{Ouchi2010}. To make this selection we consider that
a model is consistent with observations if there is a $1$-$\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. We clearly see from this Figure that the conditions imposed
by \cite{Hayashino2004} are the tightest. Comparing this Figure with
the results shown in Figure \ref{fig:restriction_mock} we see that
practically all models with $M_{\rm max}>10^{12}$ are removed. On the
other hand the comparison against \cite{Ouchi2010} does not
substantially reduce the number of models.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_meanden.pdf} 
\end{center}
\caption{Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Ouchi2010} (right). The error
bars in the theoretical data correspond to the quadratic average of
the fitting errors for each mock survey 
\label{fig:correlation_parameters}}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_meanden_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_meanden_f_occ.pdf}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_maxden_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_maxden_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}$-$f_{\rm occ}$ (right). with the models fulfilling both
   constraints on the maximal number of consistent mocks and the
  angular correlation function. Upper panels correspond
  checks the consistency with the observational data of
  \citet{Ouchi2010}. Lower panels show results after comparison
  against \citet{Hayashino2004}
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.1 &10.2 & 0.1 & 0.1\\
10.3 &10.5 & 0.1 & 0.2\\
10.4 &10.7 & 0.1 & 0.3\\
10.5 &10.6 & 0.3 & 0.1\\
10.5 &10.9 & 0.1 & 0.4\\
10.5 &11.0 & 0.1 & 0.5\\
10.6 &11.2 & 0.1 & 0.6\\
10.6 &11.4 & 0.1 & 0.8\\
10.6 &11.7 & 0.1 & 1.1\\
10.7 &11.0 & 0.2 & 0.3\\
10.8 &11.2 & 0.2 & 0.4\\
10.8 &11.3 & 0.2 & 0.5\\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.6 &10.7 &0.4 & 0.1\\
10.8 &10.9 &0.6 & 0.1\\
10.8 &11.0 &0.4 & 0.2\\
10.9 &11.0 &0.8 & 0.1\\
10.9 &11.0 &0.9 & 0.1\\
10.9 &11.1 &0.5 & 0.2\\
11.0 &11.1 &1.0 & 0.1\\
11.1 &11.3 &0.8 & 0.2\\
11.2 &11.6 &0.6 & 0.4\\
11.2 &12.2 &0.5 & 1.0\\
11.3 &11.7 &0.9 & 0.4\\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and high occupation fraction $f_{\rm occ}>0.3$.}
\end{table}

>>>>

Figure \ref{fig:correlation_parameters} shows the main results for the
best estimates of $\theta_{0}-\beta$ in the parameterization of the
ACF. Blue circles with error bars represent the results from the mocks
and the horizontal line the result from observations reported by
\cite{Ouchi2010} over a field with average number density. The
observational result does not have an uncertainty associated with
$\beta$ because the parameter was fixed in the fit. Only $40$ models
are consistent with the new constraints.

Figure \ref{fig:restriction_mock_and_f_occ_corr} we present the preferred
models in the planes $M_{\rm min}$-$M_{\rm  max}$ and $M_{\rm min}$-$f_{\rm occ}$
both for the comparisons against \cite{Hayashino2004} and
\cite{Ouchi2010}. To make this selection we consider that
a model is consistent with observations if there is a $1$-$\sigma$
overlap between both the correlation length $\theta_0$ and the power
$\beta$. We clearly see from this Figure that the conditions imposed
by \cite{Hayashino2004} are the tightest. Comparing this Figure with
the results shown in Figure \ref{fig:restriction_mock} we see that
practically all models with $M_{\rm max}>10^{12}$ are removed. On the
other hand the comparison against \cite{Ouchi2010} does not
substantially reduce the number of models.

@@

\begin{figure}
\begin{center}
\includegraphics[width=1.0\linewidth,angle=0]{power_law_correlation_degree2.pdf}  
\end{center}
\caption{Values for the free parameters $\theta_{0}$ and $\beta$
in the fitting formula (Eq. \ref{eq:fitting}) for the angular
correlation function. Blue dots correspond to simulations and the
green cross to observations by \citet{Ouchi2010} . The error
bars in the theoretical data correspond to the quadratic average of
the fitting errors for each mock
survey \label{fig:correlation_parameters}} 
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_mass.pdf}
\hspace{5mm}
\includegraphics[width=0.46\linewidth,angle=0]{Fig6_f_occ.pdf}
\end{center}
\caption{Planes $M_{\rm min}$-$M_{\rm max}$ (left) and $M_{\rm
    min}$-$f_{\rm occ}$ (right). with the models fulfilling both
   constraints on the maximal number of consistent mocks and the
  angular correlation function. The observational data correspods to
  \citet{Ouchi2010}.   
  \label{fig:restriction_mock_and_f_occ_corr}} 
\end{figure*}

@@

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.4 &10.7 & 0.1\\
 10.5 &10.6 & 0.3\\
 10.5 &10.9 & 0.1\\
 10.5 &11.0 & 0.1\\
 10.6 &10.8 & 0.2\\
 10.6 &11.2 & 0.1\\
 10.6 &11.3 & 0.1\\
 10.6 &11.4 & 0.1\\
 10.6 &11.5 & 0.1\\
 10.6 &11.6 & 0.1\\
 10.6 &11.7 & 0.1\\
 10.7 &11.0 & 0.2\\
 10.8 &11.2 & 0.2\\
 10.8 &11.3 & 0.2\\
 10.8 &11.4 & 0.2\\
 10.9 &11.3 & 0.3\\
 10.9 &11.7 & 0.2\\
 10.9 &11.8 & 0.2\\
 10.9 &11.9 & 0.2\\
 10.9 &12.0 & 0.2\\
 10.9 &12.1 & 0.2\\
 10.9 &12.2 & 0.2\\
 10.9 &12.3 & 0.2\\
 10.9 &12.6 & 0.2\\
 10.9 &12.8 & 0.2\\\hline
\end{tabular}
\end{center}
\caption{\label{table:firstfamily}List of parameters for the first
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and low
  occupation fraction $f_{\rm occ}\leq 0.3$.} 
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccc}\hline\hline
$\log_{10}M_{\rm min}$ & $\log_{10}M_{\rm max}$ & $f_{\rm occ}$ & $\Delta M$\\\hline
10.6 &10.700 & 0.4\\
 10.7 &10.8 & 0.5\\
 10.8 &10.9 & 0.6\\
 10.8 &11.0 & 0.4\\
 10.9 &11.0 & 0.8\\
 10.9 &11.0 & 0.9\\
 10.9 &11.1 & 0.5\\
 11.0 &11.1 & 1.0\\
 11.0 &11.2 & 0.6\\
 11.0 &11.4 & 0.4\\
 11.1 &11.3 & 0.7\\
 11.1 &11.3 & 0.8\\
 11.1 &11.4 & 0.6\\
 11.2 &11.4 & 0.9\\
 11.2 &11.4 & 1.0\\\hline
\end{tabular}
\end{center}
\caption{\label{table:secondfamily}List of parameters for the second
  family of models. Narrow mass range $\Delta M\leq 1.0$ dex and high occupation fraction $f_{\rm occ}>0.3$.}
\end{table}
